paper_code_documentation

### 2020-10-11 outputs/documents/notes/paper_code_documentation.Rmd
model comparison notes
updated documentation

Not able to follow through the code tutorial from Github. Google Collab code generates demo successfully.

@@

Link: https://colab.research.google.com/drive/1So95M0hHefyNm_eELglCna_ZayoDX6KV?usp=sharing

>>>>

Able to follow through the code tutorial from Github to the point to fine-tuning. Google Colab code generates demo successfully.

@@

The Google Colab demostrated text-infilling by the model after fine-tuning.
Link: https://colab.research.google.com/drive/1So95M0hHefyNm_eELglCna_ZayoDX6KV?usp=sharing
